\documentclass[12pt]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{pdfpages}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{listings} % Required for insertion of code
\usepackage{courier} % Required for the courier font

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1} % Line spacing

\newcommand{\Title}{Requirement Specification} % Assignment title
\newcommand{\Class}{Cos\ 301} % Course/class

\begin{document}

	\vspace{4em}
	
	\begin{center}%
	
	  \LARGE \bf \Title \\[4em]
	  \LARGE {\bf Group 2}\\[1em]
	  \LARGE {\bf Group Members:}\\[2em]
	  \large
	     Nico Taljaard					(10153285) \\[1em]
	     Abraham Daniel Pretorius		(12022404) \\[1em]
	     Mathys Ellis					(12019837) \\[1em]
	     Nbulungo Musetsho				(10176382) \\[1em]
	     Verushka Moodley				(29117454) \\[1em]
	     Eduan Bekker					(12214834) \\[8em]
	     {\bf Version 3.0}
	    
	\end{center}%
	
	\newpage
		{\LARGE \bf Change Log}\\[2em]
		
		\begin{tabbing}
			\hspace*{2.5cm}\=\hspace*{2.5cm}\=\hspace*{8cm}\=\hspace*{3cm} \kill
			10/02/2014 \> Version 1.0 \> Document Created \> Nico Taljaard \\
			15/02/2014 \> Version 1.0 \> System Description \> Mathys Ellis \\
			17/02/2014 \> Version 1.1 \> Edited Formatting \> Nico Taljaard \\
			17/02/2014 \> Version 1.1 \> Technical Specification \> Nbulungo Musetsho \\
			17/02/2014 \> Version 1.1 \> Created Non-functional Requirements \> Eduan Bekker \\
			18/02/2014 \> Version 1.2 \> External Interface Requirements \> Abraham Daniel Pretorius  \\
			18/02/2014 \> Version 1.2 \> Functional Requirement \> Nico Taljaard \\
			18/02/2014 \> Version 1.2 \> Updated Non-functional Requirements \> Eduan Bekker \\
			18/02/2014 \> Version 1.2 \> Updated External Interface Requirements \> Abraham Daniel Pretorius  \\
			18/02/2014 \> Version 1.2 \> Updated System Description \> Mathys Ellis \\
			20/02/2014 \> Version 1.3 \> Introduction \> Verushka Moodley \\
			20/02/2014 \> Version 1.3 \> Fixed Compile Errors \> Nico Taljaard \\
			20/02/2014 \> Version 1.2 \> Updated External Interface Requirements \> Abraham Daniel Pretorius  \\
			21/02/2014 \> Version 1.2 \> Fixed Spelling \> Nico Taljaard \\
			21/02/2014 \> Version 2.0 \> Change formatting \> Nico Taljaard \\
			23/02/2014 \> Version 2.0 \> Checked spelling and grammar \> Mathys Ellis \\
			24/02/2014 \> Version 3.0 \> Changed to new layout specification \> Nico Taljaard \\
			24/02/2014 \> Version 3.0 \> Required Functionality \> Nico Taljaard \\	
		\end{tabbing}

	\newpage
	\tableofcontents
	
	\newpage
	\section{Introduction}
	
		\vspace{0.2in}
	
	\section{Vision}
	
		\vspace{0.2in}
		
		
	
	\section{Background}
	
		\vspace{0.2in}
		
		
	
	\section{Architecture requirements}
	
		\vspace{0.2in}
		
		\subsection{Access channel requirements}
		
			\vspace{0.2in}
			
			
		
		\subsection{Quality requirements}
		
			\vspace{0.2in}
			
			
		
		\subsection{Integration requirements}
		
			\vspace{0.2in}
			
			
		
		\subsection{Architecture constraints}
	
		\vspace{0.2in}
		
		
	
	\section{Functional requirements}
	
		\vspace{0.2in}
		
		\subsection{Introduction}
		
			\vspace{0.2in}
			
			
		
		\subsection{Scope and Limitations/Exclusions}
		
			\vspace{0.2in}
			
			
		
		\subsection{Required functionality}
		
			\vspace{0.2in}
			
			\begin{flushleft}
				\textbf{Course API}
				\newline\textbf{(Priority: High, Requirement: FRQ1)}
			\end{flushleft}
			
			\vspace{0.05in}
			
				\begin{itemize}
					\item A course must be creatable.
					\item Lectures must be added to course by users with correct authorization.
					\item Lectures must be able to add Teaching assistants and Tutors to the course, aswell as be able to assign them to a practical time slot.
					\item Student information for each student that is assigned to a practical time slot of a course should be pulled from an existing database so that teaching assistants and tutors of the course can find the student to be marked.
				\end{itemize}
				
			\vspace{0.15in}
				
			\begin{flushleft}
				\textbf{Lecturer API}
				\textbf{(Priority: High, Requirement: FRQ2)}
			\end{flushleft}
			
				\begin{itemize}
					\item A tasks must be creatable for the following:
							\begin{itemize}
								\item Practicals
								\item Assignments
								\item Class tests
								\item Tests
							\end{itemize}
					\item Tasks should also contain the following information:
							\begin{itemize}
								\item Starting time to open access.
								\item End time if a specified time is required, else manual locking is required by lecture.
								\item A rubric must be added to show the mark allocation.
							\end{itemize}
					\item Adjust mark weight allocations.
					\item Lectures alone should be able to change marks of his own subjects.
					\item Assign security roles to teaching assistants and tutors.
					\item Move students to a different teaching assistant or tutor.
					\item Use the reporting API.
				\end{itemize}
				
			\vspace{0.15in}
			
			\begin{flushleft}	
				\textbf{Auditing API}
				\textbf{(Priority: High, Requirement: FRQ3)}
			\end{flushleft}
			
				\begin{itemize}
					\item Log file for following activities:
							\begin{itemize}
							 	\item Marks added by whom and when.
							 	\item Marks changed or removed by who, when and what is the reason.
							 	\item Login and logout activites
							\end{itemize}
		
					\item Lectures must be able view only the audit logs of the course(s) they are assigned to.
					\item Head of Department alone should assign a user that can view the entire change log.
					\item No edits to the audit log allowed.
				\end{itemize}
				
			\vspace{0.15in}
				
			\begin{flushleft}
				\textbf{Marking API}
				\textbf{(Priority: High, Requirement: FRQ4)}
			\end{flushleft}
			
				\begin{itemize}
					\item Accessible through mobile application for teaching assistants or tutors.
					\item Display all available mark lists for teaching assistants or tutors to mark.
					\item Within mark list display all students registered for current session with a search option.
					\item Search filters should be available for student number, surname or name. The displayed results should contain all the results that match the filters.
					\item For the selected student the marking rubric should be displayed with type able fields.
					\item Marks should be submitted to the database directly after mark has been finalized for a student.
				\end{itemize}
				
			\vspace{0.15in}
			
			\begin{flushleft}
				\textbf{Reports API}
				\textbf{(Priority: Medium-High, Requirement: FRQ5)}
			\end{flushleft}
			
				\begin{itemize}
					\item Marks can be exported in a .csv file containing the selected marks for each student.
					\item All reports should be based on a select set of marks.
					\item Numeric statistics can be exported about marks.
					\item Graphical reports should be exported to .pdf file.
				\end{itemize}
				
			\vspace{0.2in}
			
			\begin{flushleft}
				\textbf{Student API}
				\textbf{(Priority: Medium, Requirement: FRQ6)}
			\end{flushleft}
			
				\begin{itemize}
					\item Accessible through mobile application or web interface.
					\item Landing page displays all subjects of current student.
					\item Subject marks should be viewable for separate assessments as well as a progress mark of a particular course.
				\end{itemize}
				
			\vspace{0.2in}
		
		\subsection{Use case prioritization}
		
			\vspace{0.2in}
			
			
		
		\subsection{Use case/Services contracts}
		
			\vspace{0.2in}
			
			
		
		\subsection{Process specifications}
		
			\vspace{0.2in}
			
			
		
		\subsection{Domain Objects}
		
			\vspace{0.2in}
			
			
	
	\section{Open Issues}
	
		\vspace{0.2in}
		
		
	
	\section{Glossary}
	
		\vspace{0.2in}
		
	
	
\end{document}